Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex
line break second idea of pf, minor edits to 4th
modify 4th idea, \Delta -> \delta in cases, lbr 5th

\sssec*{Idea of proof:}
The construction of the $y_{i, e_i}$ in Part (a) uses Riemann--Roch
and condition ~\ref{custom:Ad-iii}. The inequality in Part (a)
follows from the fact that $\halfcan$ is similar to $\halfcan'$,
but with some of the $e_i$ incremented by $2$. Part (b) follows
because the sub-lattice spanned by $y_{i, e_i}$ and $y_{i, e_i'}$
has determinant $1$ for $i \in J$, so the generators in Part (a)
generate all of $R_\halfcan$ over $R_{\halfcan'}$. To check part (c),
we construct relations between the generators of $R_{\halfcan}$
over $R_{\halfcan'}$: we note that an element lies in $R_{\halfcan'}$
if and only if its pole order at $P_i$ for $i \in J$ is not too
large, and use Lemma ~\ref{lem:admissible_inequality} to bound pole
orders. Part (d) follows fairly easily from the definition of
admissibility.

@@

\begin{proof}
If $\Delta = 0$, the result is immediate from Reid \cite[Theorem 3.4]
{reid:infinitesimal}. Otherwise, if $\Delta > 0$, the bound on the
degrees of minimal generators follows from Lemma
~\ref{lem:generation-5}, while the bound on the degrees of minimal
relations follows from Proposition ~\ref{prop:relation-10}.
\end{proof}

@@

\sssec*{Idea of Proof:}
We check the theorem in two cases, depending on whether $\Delta > 0$.
If $\Delta > 0$, we first check that the theorem holds for $\halfcan_X$
by inductively adding in log points to the base case of $\halfcan_X'
= 0$. Then we check that it holds for $\halfcan$ by raising
the stabilizer orders of stacky points in a sequence of steps. When
raising the stacky orders, it is important that we increment the
stabilizer orders of the maximum possible number of stacky points
at each step, so that the corresponding set will remain admissible.
The check for $\Delta = 0$ is similar, although in this case we do
not need to add in log points, only stacky points, and we will need
to utilize the base cases from Subsection ~\ref{ssec:g-1_base}.

@@

\vskip.1in
\noindent
{\sf Case 1: $\Delta > 0$}

If $\Delta > 0$, we must have $\Delta \geq 2$, by Remark ~\ref{rem:delta-not-1}. In this case, let $\halfcan_X \in \di X$ satisfy $2 \halfcan_X \sim K_X + \Delta$. We have $\deg \halfcan_X \geq 1$, so, by Riemann--Roch, $h^0(\sx, \halfcan) \geq 1.$ Therefore, $\halfcan$ is linearly equivalent to an effective divisor. Thus, without loss of generality, we may assume $\halfcan$ is an effective divisor.

@@

To complete the case that $\Delta > 0$, we now need show the theorem holds for a \emph{stacky} log spin canonical divisor $\halfcan$.  It suffices to show that if the theorem holds for a log spin canonical divisor $\halfcan'$ with $\deg \lfloor L' \rfloor > 0$, then it holds for $L' + \subhalf {e_i}P_i$ with $e_i$ odd.  As above, if $P$ is not a basepoint of $\halfcan'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-1}. On the other hand, if $P$ is a basepoint of $\halfcan'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-2}.

\vskip.1in
\noindent
{\sf Case 2: $\Delta = 0$}

Since $\Delta = 0$, we may write $\halfcan = \halfcan_X + \sum_{i = 1}^{r}\subhalf{e_i}P_i.$ There are now two further subcases, depending on whether $\halfcan_X = 0$ or $\halfcan_X = P - Q$ for $P$ and $Q$ two distinct hyperelliptic fixed  points.

@@

Second, we deal with the case that $\sx$ has at least two stacky points. 
If $(\sx', \delta, \halfcan')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then as found in 
Example ~\ref{eg:base-1-33}, the triple $(\sx', 0, P-Q + \frac{1}{3}P_1+\frac{1}{3}P_2)$
satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
Therefore, applying Lemma ~\ref{lem:sat-2} $r-2$ times, we see that the theorem holds for $(\sx', \delta', \halfcan')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i.$ 
Finally, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds 
for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.

@@

\sssec*{Idea of proof:} The method of this proof is almost identical to that of Theorem ~\ref{thm:g-1-main}. When $\delta > 0$, we first add in log points, and then increment the stabilizer orders of stacky points, checking that the theorem holds at each step. The more technical case occurs when $\delta = 0$, in which case we simply increment the stabilizer orders of stacky points starting from one of our base cases, and check that every stacky curve can be reached by a sequence of admissible incrementations from a base case.

>>>>

\sssec*{Idea of Proof:}
The construction of the $y_{i, e_i}$ in Part (a) uses Riemann--Roch
and condition ~\ref{custom:Ad-iii}. The inequality in Part (a)
follows from the fact that $\halfcan$ is similar to $\halfcan'$,
but with some of the $e_i$ incremented by $2$. Part (b) follows
because the sub-lattice spanned by $y_{i, e_i}$ and $y_{i, e_i'}$
has determinant $1$ for $i \in J$, so the generators in Part (a)
generate all of $R_\halfcan$ over $R_{\halfcan'}$. To check part (c),
we construct relations between the generators of $R_{\halfcan}$
over $R_{\halfcan'}$: we note that an element lies in $R_{\halfcan'}$
if and only if its pole order at $P_i$ for $i \in J$ is not too
large, and use Lemma ~\ref{lem:admissible_inequality} to bound pole
orders. Part (d) follows fairly easily from the definition of
admissibility.

@@

\begin{proof}
If $\delta = 0$, the result is immediate from Reid \cite[Theorem 3.4]
{reid:infinitesimal}. Otherwise, if $\delta > 0$, the bound on the
degrees of minimal generators follows from Lemma
~\ref{lem:generation-5}, while the bound on the degrees of minimal
relations follows from Proposition ~\ref{prop:relation-10}.
\end{proof}

@@

\sssec*{Idea of Proof:}
We check the theorem in two cases, depending on whether $\delta > 0$.
If $\delta > 0$, we first check that the theorem holds for
$\halfcan_X$ by inductively adding in log points to the base case of$
\halfcan_X' = 0$. Then we check that the theorem holds for $\halfcan$
by adding stacky points and then inductively raising the 
stabilizer orders of stacky points in the following sequence of 
steps. When raising the stacky orders, it is important that we 
increment the stabilizer orders of as many stacky points as 
possible to maintain admissibility for the maximal possible sets of 
stacky points. Then, we may also use the fact that raising the 
stabilizer orders of any subset of these maximal sets of stacky 
points will still preserve admissibility.

The check for $\delta = 0$ is similar, although in this case we do
not need to add in log points, only stacky points, and we will need
to utilize the base cases from Subsection ~\ref{ssec:g-1_base}.

@@

\vskip.1in
\noindent
{\sf Case 1: $\delta > 0$}

If $\delta > 0$, we must have $\delta \geq 2$, by Remark ~\ref{rem:delta-not-1}. In this case, let $\halfcan_X \in \di X$ satisfy $2 \halfcan_X \sim K_X + \Delta$. We have $\deg \halfcan_X \geq 1$, so, by Riemann--Roch, $h^0(\sx, \halfcan) \geq 1.$ Therefore, $\halfcan$ is linearly equivalent to an effective divisor. Thus, without loss of generality, we may assume $\halfcan$ is an effective divisor.

@@

To complete the case that $\delta > 0$, we now need show the theorem holds for a \emph{stacky} log spin canonical divisor $\halfcan$.  It suffices to show that if the theorem holds for a log spin canonical divisor $\halfcan'$ with $\deg \lfloor L' \rfloor > 0$, then it holds for $L' + \subhalf {e_i}P_i$ with $e_i$ odd.  As above, if $P$ is not a basepoint of $\halfcan'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-1}. On the other hand, if $P$ is a basepoint of $\halfcan'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-2}.

\vskip.1in
\noindent
{\sf Case 2: $\delta = 0$}

Since $\delta = 0$, we may write $\halfcan = \halfcan_X + \sum_{i = 1}^{r}\subhalf{e_i}P_i.$ There are now two further subcases, depending on whether $\halfcan_X = 0$ or $\halfcan_X = P - Q$ for $P$ and $Q$ two distinct hyperelliptic fixed  points.

@@

Second, we deal with the case that $\sx$ has at least two stacky points. 
If $(\sx', \Delta, \halfcan')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then as found in 
Example ~\ref{eg:base-1-33}, the triple $(\sx', 0, P-Q + \frac{1}{3}P_1+\frac{1}{3}P_2)$
satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
Therefore, applying Lemma ~\ref{lem:sat-2} $r-2$ times, we see that the theorem holds for $(\sx', \Delta', \halfcan')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i.$ 
Finally, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds 
for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.

@@

\sssec*{Idea of Proof:}
The method of this proof is almost identical to that of Theorem
~\ref{thm:g-1-main}. When $\delta > 0$, we first add in log points,
and then increment the stabilizer orders of stacky points, checking
that the theorem holds at each step. The more technical case occurs
when $\delta = 0$, in which case we simply increment the stabilizer
orders of stacky points starting from one of our base cases, and
check that every stacky curve can be reached by a sequence of
admissible incrementations from a base case.
